\noindent\textbf{Published:}

Xiang Ying, \textbf{Xiaoning Wang}, Ying He. Saddle vertex graph (SVG): a novel solution to the discrete geodesic problem. \textit{ACM Transactions on Graphics (Proceedings of ACM SIGGRAPH ASIA 2013)}, Vol. 32, No. 6, pp. 170:1-170:12, 2013.

Shi-Qing Xin, \textbf{Xiaoning Wang}, Jiazhi Xia, Wolfgang Mueller-Wittig, Guo-Jin Wang, Ying He. Parallel computing 2D Voronoi diagrams using untransformed sweepcircles. \textit{Computer-Aided Design (CAD)}, Vol. 45, No. 1, pp. 483-493, 2013.

\textbf{Xiaoning Wang}, Xiang Ying, Yong-Jin Liu, Shi-Qing Xin, Wenping Wang, Xianfeng Gu, Wolfgang Mueller-Wittig, Ying He. Intrinsic computation of centroidal Voronoi tessellation (CVT) on meshes, \textit{Computer-Aided Design (CAD)}, Vol. 58, No. 1, pp. 51-61, 2015. \textbf{(Best Paper Award 3rd Place in Solid and Physical Modeling 2014)}

Yuen Shan Leung, \textbf{Xiaoning Wang}, Ying He, Yong-Jin Liu, Charlie C.L. Wang. Robust and GPU-friendly Isotropic Meshing Based on Narrow-banded Euclidean Distance Transformation. Pacific Graphics 2015. (Short Paper)

Peihong Guo, Ergun Akleman, He Ying, \textbf{Xiaoning Wang}, and Wei Liu. 2015. Critical points with discrete Morse theory. ACM SIGGRAPH 2015 Posters, 67:1-67:1, 2015.

\noindent\textbf{Ready to submit:}

\textbf{Xiaoning Wang}, Le Tien Hung, Qian Sun, Xiang Ying, Wolfgang Mueller-witting, Ying He. User Controllable Anisotropic Shape Distribution on 3D Meshes.
.
A General Graph-Theoretic Framework for Computing Discrete Geodesics.





